Radio Emission from Red-Giant Hot Jupiters

### 2015-12-19 ms.tex
minor edits

\revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. ??
%While interacting with magnetic field, the ionized portion could lose their energy 
%Therefore, some part of the incoming wind particles are what we could envision is the 
%Considering other uncertainties of radio wave generation, we 
The detailed electromagnetic structure around RGHJs therefore requires an elaborate numerical simulations, which is beyond the scope of this paper. Noting that all other uncertainties including the radio wave generation, in this paper we simply aim at giving an order-of-magnitude estimate. }

>>>>

\revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
%While interacting with magnetic field, the ionized portion could lose their energy 
%Therefore, some part of the incoming wind particles are what we could envision is the 
%Considering other uncertainties of radio wave generation, we 
The detailed electromagnetic structure around RGHJs therefore requires  elaborate numerical simulations, which is beyond the scope of this paper. Noting that all other uncertainties, in this paper we simply aim at giving an order-of-magnitude estimate. }
